A quantum parallel Markov chain Monte Carlo

### 2023-01-18 main.tex
first paragraph of blackhole section

\subsubsection{Bayesian image something}\label{sec:bayesIm}

@@

>>>>

\subsubsection{Bayesian image analysis}\label{sec:bayesIm}

@@

We apply a Bayesian image analysis model from \citet{hurn1997difficulties} to an intensity map (Figure \ref{fig:blackHole}) of the newly imaged supermassive black hole, Sagittarius A*, located at the Galactic Center of the Milky Way \citep{akiyama2022first}.  Whereas one cannot see the black hole itself, one may see the shadow of the black hole cast by the hot, swirling cloud of gas surrounding it.  We use Bayesian image analysis to extract the black hole from the surrounding cloud.

\begin{itemize}
	\item data in [1,255]
	\item model
	\item mcmc
\end{itemize}
